---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

[![Travis-CI Build Status](https://travis-ci.org/jjchern/gglorenz.svg?branch=master)](https://travis-ci.org/jjchern/gglorenz)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/jjchern/gglorenz?branch=master&svg=true)](https://ci.appveyor.com/project/jjchern/gglorenz)

# About `gglorenz`

The goal of `gglorenz` is to plot Lorenz Curves with the blessing of `ggplot2`.

# Installation

```R
# Install the CRAN version
install.packages("gglorenz")

# Install the development version from GitHub:
# install.packages("remotes")
remotes::install_github("jjchern/gglorenz")
```

# Example

Suppose you have a vector with each element representing the amount the stuff a person produced, and you are interested in knowing how much stuff are produced by the top x% of the people, then the `gglorenz::stat_lorenz(desc = TRUE)` would make a graph for you.

```{r}
library(tidyverse)
library(gglorenz)

billionaires

billionaires %>%
    ggplot(aes(TNW)) +
    stat_lorenz(desc = TRUE) +
    coord_fixed() +
    geom_abline(linetype = "dashed") +
    theme_minimal() +
    hrbrthemes::scale_x_percent() +
    hrbrthemes::scale_y_percent() +
    hrbrthemes::theme_ipsum() +
    labs(x = "Cumulative Percentage of the Top 500 Billionaires",
         y = "Cumulative Percentage of Total Net Worth",
         title = "Inequality Among Billionaires",
         caption = "Source: https://www.bloomberg.com/billionaires/ (accessed February 8, 2018)")

billionaires %>%
    filter(Industry %in% c("Technology", "Real Estate")) %>%
    ggplot(aes(x = TNW, colour = Industry)) +
    stat_lorenz(desc = TRUE) +
    coord_fixed() +
    geom_abline(linetype = "dashed") +
    theme_minimal() +
    hrbrthemes::scale_x_percent() +
    hrbrthemes::scale_y_percent() +
    hrbrthemes::theme_ipsum() +
    labs(x = "Cumulative Percentage of Billionaires",
         y = "Cumulative Percentage of Total Net Worth",
         title = "Real Estate is a Relatively Equal Field",
         caption = "Source: https://www.bloomberg.com/billionaires/ (accessed February 8, 2018)")
```

You can also use other geoms such as `area` or `polygon` and arranging population in ascending order:

```{r}
billionaires %>%
    filter(Industry %in% c("Technology", "Real Estate")) %>% 
    add_row(Industry = "Perfect Equality", TNW = 1) %>% 
    ggplot(aes(x = TNW, fill = Industry)) +
    stat_lorenz(geom = "area", alpha = 0.65) +
    coord_fixed() +
    hrbrthemes::scale_x_percent() +
    hrbrthemes::scale_y_percent() +
    hrbrthemes::theme_ipsum() +
    theme(legend.title = element_blank()) +
    labs(x = "Cumulative Percentage of Billionaires",
         y = "Cumulative Percentage of Total Net Worth",
         title = "Real Estate is a Relatively Equal Field",
         caption = "Source: https://www.bloomberg.com/billionaires/ (accessed February 8, 2018)")

billionaires %>%
    filter(Industry %in% c("Technology", "Real Estate")) %>% 
    mutate(Industry = forcats::as_factor(Industry)) %>% 
    ggplot(aes(x = TNW, fill = Industry)) +
    stat_lorenz(geom = "polygon", alpha = 0.65) +
    geom_abline(linetype = "dashed") +
    coord_fixed() +
    hrbrthemes::scale_x_percent() +
    hrbrthemes::scale_y_percent() +
    hrbrthemes::theme_ipsum() +
    theme(legend.title = element_blank()) +
    labs(x = "Cumulative Percentage of Billionaires",
         y = "Cumulative Percentage of Total Net Worth",
         title = "Real Estate is a Relatively Equal Field",
         caption = "Source: https://www.bloomberg.com/billionaires/ (accessed February 8, 2018)")
```

# Acknowledgement

The package came to exist solely because Bob Rudis was [generous enough](https://github.com/hrbrmstr/ggalt/issues/46) to write a chapter that [demystifies `ggplot2`.](https://rud.is/books/creating-ggplot2-extensions/demystifying-ggplot2.html)
